Creating More Meaningful Explanations for Audio Deepfake Detection

### 2025-03-05 draft.tex
changes to metric definitions

In order to contextualize the metrics, we will make the following definitions.
    \begin{itemize}
        \item Let \(S\) be the set of samples with \(s \in S\) as an element of the set.
        \item Let \(F\) be the set of features with \(f \in F\) as an element of the set.
        \item Let \(w_{fs}\) be the weight value of feature \(f\) of sample \(s\) as
            produced by the explainer.
        \item Let \(l_{s}\) be the correct label of the sample \(s\).
    \end{itemize}
The first metric we propose is the mean of the absolute values of the weights of each feature within a set of explanations.
% The first metric we will define is the mean of the absolute values of the weights of the explanations, summarized along the sample axis, delivering one value per feature. 
We will further refer to this metric as importance, and we define it mathematically as follows for every feature \(f \in F\):
\begin{equation}
    Imp(f) = \frac{\sum_{s \in S} |w_{fs}|}{|S|}.
\end{equation}

The second metric we will define is the average aggregate correctness on a per-feature basis, which we will further refer to as trust. The trust per feature \(f \in F\) can be defined as follows:
\begin{equation}
    Trust(f) = \frac{\sum_{s \in S} w_{fs}(2l_{s}-1)}{|S|}.
\end{equation}

>>>>

In order to contextualize the metrics, we will make the following definitions.
    \begin{itemize}
        \item Let \(S\) be the set of samples with \(s \in S\) as an element of the set.
        \item Let \(F\) be the set of features with \(f \in F\) as an element of the set.
        \item Let \(w_{fs}\) be the weight value of feature \(f\) of sample \(s\) as
            produced by the explainer.
        \item Let \(l_{s}\) be the correct label of the sample \(s\).
    \end{itemize}
The first metric we propose is the mean of the absolute values of the weights of each feature within a set of explanations.
% The first metric we will define is the mean of the absolute values of the weights of the explanations, summarized along the sample axis, delivering one value per feature. 
We will further refer to this metric as importance, and we define it mathematically as follows for every feature \(f \in F\) extracted from sample \(s \in S\):
\begin{equation}
    Imp(f, s) = \frac{\sum_{s \in S} |w_{fs}|}{|S|}.
\end{equation}

The second metric we will define is the average aggregate correctness on a per-feature basis, which we will further refer to as trust. The trust per feature \(f \in F\) extracted from sample \(s \in S \) can be defined as follows:
\begin{equation}
    Trust(f, s) = \frac{\sum_{s \in S} w_{fs}(2l_{s}-1)}{|S|}.
\end{equation}
